Resurgence of the Airy function \\ and other exponential integrals

### 2022-04-01 draft2.tex
Keep working on outline

This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside. We can, however, set aside any finite set of them. \color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.]} For each cutoff $N$, the tail
\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]

>>>>

This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside. We can, however, set aside any finite set of them. \color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots. See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]

### 2022-04-01 exp-resurgence.tex
Keep working on outline

\color{orange}
\textbf{Veronica's proposal}

@@

\begin{enumerate}
\item what are exponential integrals? Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}). In physics ?? \textcolor{gray}{has to be done}
\item what does it mean being Borel regular? and when does it happen? \textcolor{gray}{has to be done}
\begin{itemize}
\item Watson condition
\item linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday--Richaud ?, big idea in {\tt airy-resurgence}]
\item our theorem [{\tt draft2}]
\end{itemize}
\item Resurgence of exponential integrals and Stokes phenomena
\begin{itemize}
\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
\item ODE and fractional derivative formula [{\tt draft2}]: hypergeometric functions \textcolor{gray}{has to be done}
\end{itemize}
\item The Airy example
\begin{itemize}
\item $I(z)$ is a solution of a linear ODE. We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
\item Stokes constants using fractional derivative formula and Borel transform computation [{\tt draft2}]
\item Comparison with the literature (Marino, Sauzin, Kontsevich slides) \textcolor{gray}{has to be done}
\end{itemize}
\item Bessel $1/n$ (follows from Airy) we compute Borel transform and Stokes constants \textcolor{gray}{has to be done}
\item Bessel 0 (it is different because we have infinite cover) we compute Stokes constants [{\tt draft2}]
\item Bessel $\mu$ (follows from Bessel 0) we compute Stokes constants [{\tt modified Bessel}]
\end{enumerate}

>>>>

\color{orange}
\section*{Veronica's proposal}

@@

\begin{enumerate}
\item introduction
\begin{itemize}
\item what are exponential integrals? \textcolor{gray}{has to be done}
\begin{itemize}
\item motivation
\begin{itemize}
\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
\item In physics ??
\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
\end{itemize}
\end{itemize}
\item Borel regularity
\begin{itemize}
\item what does it mean being Borel regular?
\item when does it happen?
\begin{itemize}
\item Recall Watson condition (old)
\item State new Borel regularity results
\begin{itemize}
\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday-Richaud ?, big idea in {\tt airy-resurgence}]
\item Thimble integral [{\tt draft2}]
\end{itemize}
\end{itemize}
\end{itemize}
\item State results about resurgence of exponential integrals and Stokes phenomena
\begin{itemize}
\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
\item ODE and fractional derivative formula [{\tt draft2}]
\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
\end{itemize}
\end{itemize}
\item Formalism for Laplace transform
\begin{enumerate}
\item Introduction
\begin{enumerate}
\item
\end{enumerate}
\end{enumerate}
\item General cases
\begin{enumerate}
\item Borel regularity
\begin{itemize}
\item General ODE of the form
\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
\item General thimble integral (conditions?)
\end{itemize}
\item Resurgence
\end{enumerate}
\item The Airy example
\begin{itemize}
\item $I(z)$ is a solution of a linear ODE. We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
\item Stokes constants using fractional derivative formula and Borel transform computation [{\tt draft2}]
\item Comparison with the literature (Marino, Sauzin, Kontsevich slides) \textcolor{gray}{has to be done}
\end{itemize}
\item Bessel $1/n$ (follows from Airy) we compute Borel transform and Stokes constants \textcolor{gray}{has to be done}
\item Bessel 0 (it is different because we have infinite cover) we compute Stokes constants [{\tt draft2}]
\item Bessel $\mu$ (follows from Bessel 0) we compute Stokes constants [{\tt modified Bessel}]
\end{enumerate}
